Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-23 paper/paper.tex
Jarek's final edits. ready for submission

The goal of this workflow ensemble scheduling and cloud provisioning problem is
to complete as many high-priority workflows as possible given a fixed budget and
deadline. Only workflows for which all tasks are finished by the deadline are 
considered to be complete---partial results are not usable in this model.

@@

\begin{figure*}[t] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Number of workflows completed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows, {\em small budget}
(top) and {\em large budget} (bottom). The ranges on $y$ axis are chosen to 
emphasize the differences the performance of the algorithms.}
\label{fig:number-complete-pareto}
\end{figure*}

@@

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences the performance of the algorithms.}
\label{fig:cost}
\end{figure*}

@@

We believe that the results of our study can be applied in practice to develop 
tools that assist researchers in planning their large-scale computational
experiments. The estimates of costs, runtimes and number of workflows completed
that can be obtained from both the static algorithms and from the simulation
runs, constitute valuable hints for the planning decisions and assessing the
associated trade-offs. For this purpose our future work includes also further
extension of our experimental studies~\cite{Juve2009,vockler11} of workflows on
available cloud infrastructures to develop more accurate performance and cost
models of the applications. This should lead to better understanding of theproblems and costs of doing science in the cloud.

>>>>

The goal of the workflow ensemble scheduling and cloud provisioning problem
considered in this paper is to complete as many high-priority workflows as
possible given a fixed budget and deadline. Only workflows for which all tasks
are finished by the deadline are considered to be complete---partial results are
not usable in this model.

@@

\begin{figure*}[t] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Number of workflows completed for DPDS, AW-DPDS and SPSS
algorithms on ensembles of 100 Pareto-distributed workflows, {\em small budget}
(top) and {\em large budget} (bottom). The ranges on $y$ axis are chosen to 
emphasize the differences between the performance of the algorithms.}
\label{fig:number-complete-pareto}
\end{figure*}

@@

\begin{figure*}[htb] 
\centering
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=0.19\textwidth]{figures/pareto-cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences  between  the performance of the algorithms.}
\label{fig:cost}
\end{figure*}

@@

We believe that the results of our study can be applied in practice to develop 
tools that assist researchers in planning their large-scale computational
experiments. The estimates of costs, runtimes and number of workflows completed
that can be obtained from both the static algorithms and from the simulation
runs, constitute valuable hints for the planning decisions and assessing the
associated trade-offs. For this purpose our future work includes also further
extension of our experimental studies~\cite{Juve2009,vockler11} of workflows on
available cloud infrastructures to develop more accurate performance and cost
models of the applications. This should lead to better understanding of the
problems and costs of doing science in the cloud.
